---
title: "Data Viz Final Presentation"
author: "Moises Escobar, Justin Ko, Yiwei Li, Kexu Duan"
date: "2023-05-03"
output: html_document
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message = FALSE, warning = FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(geojsonio)
library(leaflet)
library(DT)
library(shiny)
library(RColorBrewer)
library(readr)
library(leaflet.extras)
library(sf)
library(RColorBrewer)
library(plotly)
library(readr)
library(tidyverse)
library(lubridate)
library(stringr)
library(wordcloud2)
library(countrycode)
library(ggimage)
```

```{r, message = FALSE, warning = FALSE}
centiment <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/centiment_survey.xlsx")
analysis <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/survey_analysis.xlsx")
states <- geojsonio::geojson_read("https://rstudio.github.io/leaflet/json/us-states.geojson",
                                  what = "sp")
obesity_11 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_11.xlsx")
obesity_12 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_12.xlsx")
obesity_13 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_13.xlsx")
obesity_14 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_14.xlsx")
obesity_15 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_15.xlsx")
obesity_16 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_16.xlsx")
obesity_17 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_17.xlsx")
obesity_18 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_18.xlsx")
obesity_19 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_19.xlsx")
obesity_20 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_20.xlsx")
obesity_21 <- read_excel("/Users/justin/Downloads/drive-download-20230503T031622Z-001/state_obesity_21.xlsx")
```


```{r, message = FALSE, warning = FALSE}
# EDA
lbs_to_kg <- 2.20462
in_to_ft <- 12
in_to_m <- 39.3701
cent_final <- centiment %>%
  mutate(weight_kg = `Weight (in pounds)` / lbs_to_kg,
         height_ft = as.numeric(`Height (in feet and inches) Feet`),
         height_in = as.numeric(`Height (in feet and inches) Inches`),
         height_m = (height_ft * in_to_ft + height_in) / in_to_m,
         bmi = weight_kg / height_m^2) %>%
  cbind(analysis)

# U.S. Map 2011
states@data <- cbind(states@data, obesity_11)
states_11 <- states 

# U.S. Map 2012
states@data <- cbind(states@data, obesity_12)
states_12 <- states

# U.S. Map 2013
states@data <- cbind(states@data, obesity_13)
states_13 <- states

# U.S. Map 2014
states@data <- cbind(states@data, obesity_14)
states_14 <- states

# U.S. Map 2015
states@data <- cbind(states@data, obesity_15)
states_15 <- states

# U.S. Map 2016
states@data <- cbind(states@data, obesity_16)
states_16 <- states

# U.S. Map 2017
states@data <- cbind(states@data, obesity_17)
states_17 <- states

# U.S. Map 2018
states@data <- cbind(states@data, obesity_18)
states_18 <- states

# U.S. Map 2019
states@data <- cbind(states@data, obesity_19)
states_19 <- states

# U.S. Map 2020
states@data <- cbind(states@data, obesity_20)
states_20 <- states

# U.S. Map 2021
states@data <- cbind(states@data, obesity_21)
states_21 <- states
```

## Current Problem
### Obesity Heatmap
```{r, message = FALSE, warning = FALSE}
bins <- c(20, 23, 26, 29, 32, 35, 38, 41, 44)
pal <- colorBin("YlOrRd", domain = states$obesity_11, bins = bins)

# 2011
labels_11 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_11@data$name, states_11@data$obesity_11
) %>% lapply(htmltools::HTML)

o_11 <- leaflet(states_11) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_11),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_11,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_11, opacity = 0.7, title = NULL,
    position = "bottomright")
o_11

# 2012
labels_12 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_12$name, states_12$obesity_12
) %>% lapply(htmltools::HTML)

o_12 <- leaflet(states_12) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_12),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_12,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_12, opacity = 0.7, title = NULL,
    position = "bottomright")
o_12

# 2013
labels_13 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_13$name, states_13$obesity_13
) %>% lapply(htmltools::HTML)

o_13 <- leaflet(states_13) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_13),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_13,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_13, opacity = 0.7, title = NULL,
    position = "bottomright")
o_13

# 2014
labels_14 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_14$name, states_14$obesity_14
) %>% lapply(htmltools::HTML)

o_14 <- leaflet(states_14) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_14),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_14,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_14, opacity = 0.7, title = NULL,
    position = "bottomright")
o_14

# 2015
labels_15 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_15$name, states_15$obesity_15
) %>% lapply(htmltools::HTML)

o_15 <- leaflet(states_15) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_15),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_15,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_15, opacity = 0.7, title = NULL,
    position = "bottomright")
o_15

# 2016
labels_16 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_16$name, states_16$obesity_16
) %>% lapply(htmltools::HTML)

o_16 <- leaflet(states_16) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_16),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_16,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_16, opacity = 0.7, title = NULL,
    position = "bottomright")
o_16

# 2017
labels_17 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_17$name, states_17$obesity_17
) %>% lapply(htmltools::HTML)

o_17 <- leaflet(states_17) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_17),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_17,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_17, opacity = 0.7, title = NULL,
    position = "bottomright")
o_17

# 2018
labels_18 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_18$name, states_18$obesity_18
) %>% lapply(htmltools::HTML)

o_18 <- leaflet(states_18) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_18),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_18,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_18, opacity = 0.7, title = NULL,
    position = "bottomright")
o_18

# 2019
labels_19 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_19$name, states_19$obesity_19
) %>% lapply(htmltools::HTML)

o_19 <- leaflet(states_19) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_19),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_19,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_19, opacity = 0.7, title = NULL,
    position = "bottomright")
o_19

# 2020
labels_20 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_20$name, states_20$obesity_20
) %>% lapply(htmltools::HTML)

o_20 <- leaflet(states_20) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_20),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_20,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_20, opacity = 0.7, title = NULL,
    position = "bottomright")
o_20

# 2021
labels_21 <- sprintf(
  "<strong>%s</strong><br/>%g percent",
  states_21$name, states_21$obesity_21
) %>% lapply(htmltools::HTML)

o_21 <- leaflet(states_21) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(obesity_21),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_21,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~obesity_21, opacity = 0.7, title = NULL,
    position = "bottomright")
o_21
```

### BMI of Americans
```{r, message = F, warning = F}
annotation <- data.frame(
   x = c(17),
   y = c(48),
   label = c("Healthy Range")
)

ggplot(data=cent_final, aes(x = bmi)) +
  geom_histogram(fill='#848884') +
  annotate("rect", fill = "#184E77", alpha = 0.6, 
        xmin = 18.5, xmax = 24.9,
        ymin = 0, ymax = Inf) + 
  geom_label(data = annotation, aes(x=x, y=y, label=label)) + 
  # geom_vline(xintercept = 18.5, linetype="dashed", color = "#168AAD", size=1.5) +
  # geom_vline(xintercept = 24.9, linetype="dashed", color = "#168AAD", size=1.5) +
  theme_minimal() + 
  labs(x = 'BMI', y='Count', title="Histogram of respondents' BMI")
```

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Challenges to healthier diets 
### Fast Food Restaurants Across NYC
```{r, message = FALSE, warning = FALSE}
# Import dataset
FastFoodRestaurants <- read_csv("/Users/justin/Downloads/US_Fast_Food_Restaurants - Sheet1.csv")

# Filter data by specific state (e.g., New York) and latitude and longitude bounds
FastFoodRestaurants_NY <- FastFoodRestaurants %>% 
  filter(province == "NY" & 
         latitude >= 40.0 & latitude <= 41.0 &
         longitude >= -75.5 & longitude <= -73.5) %>%
 mutate(name = ifelse(name == "SUBWAY", "Subway", name))

# Define a color palette based on the unique restaurant names
color_palette <- colorFactor(palette = "viridis", domain = unique(FastFoodRestaurants_NY$name))

# Set the image URLs to the hosted images
mcdonalds_logo_url <- "https://upload.wikimedia.org/wikipedia/commons/5/50/McDonald%27s_SVG_logo.svg"
subway_logo_url <- "https://1000logos.net/wp-content/uploads/2017/06/Subway-logo.png"
dunkin_donuts_logo_url <- "https://i.pinimg.com/originals/5a/f4/2b/5af42b2e31010a24ac46d2cb5a0e60a6.png"
burger_king_logo_url <- "https://upload.wikimedia.org/wikipedia/commons/8/85/Burger_King_logo_%281999%29.svg"
taco_bell_logo_url <- "https://1000logos.net/wp-content/uploads/2017/06/Taco-Bell-Logo-1024x640.png"
kfc_logo_url <- "https://1000logos.net/wp-content/uploads/2017/03/Kfc_logo-768x432.png"
# Set the image URLs for the new restaurants
boston_market_logo_url <- "https://cdn.freebiesupply.com/logos/large/2x/boston-market-2-logo-png-transparent.png"
fuku_logo_url <- "https://eatfuku.com/wp-content/themes/fuku-3/images/logo.svg"
dominos_pizza_logo_url <- "https://1000logos.net/wp-content/uploads/2023/04/Dominos-logo.png"
baskin_robbins_logo_url <- "https://upload.wikimedia.org/wikipedia/commons/thumb/9/97/Baskin-Robbins_logo_2022.svg/2880px-Baskin-Robbins_logo_2022.svg.png"
panera_bread_logo_url <- "https://logos-download.com/wp-content/uploads/2016/11/Panera_Bread_logo_symbol.png"
wendys_logo_url <- "https://www.mashed.com/img/gallery/dont-believe-this-myth-about-the-wendys-logo/intro-1611697081.jpg"
chipotle_mexican_grill_logo_url <- "https://upload.wikimedia.org/wikipedia/en/thumb/3/3b/Chipotle_Mexican_Grill_logo.svg/1200px-Chipotle_Mexican_Grill_logo.svg.png"
little_caesars_pizza_logo_url <- "https://www.gaylordmichigan.net/wp-content/uploads/2017/06/Untitled-design-2023-03-22T114407.307.png"
popeyes_logo_url <- "https://upload.wikimedia.org/wikipedia/commons/thumb/7/73/Popeyes_logo.svg/1200px-Popeyes_logo.svg.png"
five_guys_logo_url <- "https://dynl.mktgcdn.com/p/FIoFKEm46-afGyd-Yl2FKX-ma356Q63KQxQ-4kDqcng/1001x1001.png"
sbarro_logo_url <- "https://upload.wikimedia.org/wikipedia/commons/thumb/e/ef/Sbarro_logo.svg/1200px-Sbarro_logo.svg.png"
git_it_n_git_logo_url <- "https://media-cdn.grubhub.com/image/upload/d_search:browse-images:default.jpg/w_80,q_80,fl_lossy,dpr_2.0,c_fit,f_auto,h_80/w8jzu4c4zofnvdof6ssi"
b_good_logo_url <- "https://mma.prnewswire.com/media/558745/BGOOD_Logo.jpg?p=twitter"
thirty_first_avenue_gyro_logo_url <- "https://media-cdn.grubhub.com/image/upload/d_search:browse-images:default.jpg/w_80,q_80,fl_lossy,dpr_2.0,c_fit,f_auto,h_80/wopcjumnf4dvzvyj8tej"
arbys_logo_url <- "https://upload.wikimedia.org/wikipedia/commons/f/f4/Arby%27s_logo.svg"
smashburger_logo_url <- "https://nmgprod.s3.amazonaws.com/media/files/79/8e/798ee36529dc2cdc121456549c0b0051/cover_image_1617194867.png.760x400_q85_crop_upscale.png"
white_castle_logo_url <- "https://logodownload.org/wp-content/uploads/2021/05/white-castle-logo.png"
kennedy_fried_chicken_pizza_logo_url <- "https://media-cdn.grubhub.com/image/upload/d_search:browse-images:default.jpg/w_300,q_100,fl_lossy,dpr_2.0,c_fit,f_auto,h_300/iu3ttxzx4yppjmzszpct"
dairy_queen_logo_url <- "https://cdn.lovesavingsgroup.com/logos/dq.png"
blimpie_logo_url <- "https://searchvectorlogo.com/wp-content/uploads/2021/02/blimpie-americas-sub-shop-logo-vector.png"
nathans_famous_logo_url <- "https://mms.businesswire.com/media/20221214005201/en/1663867/5/Nathan%27s_Famous_Logos-27.jpg"
pizza_hut_logo_url <- "https://upload.wikimedia.org/wikipedia/sco/thumb/d/d2/Pizza_Hut_logo.svg/2177px-Pizza_Hut_logo.svg.png"
wendys_logo_url <- "https://www.clipartmax.com/png/middle/157-1572782_wendys-wendys-logo-png.png"
papa_johns_logo_url <- "https://cdn.freebiesupply.com/logos/large/2x/papa-johns-pizza-1-logo-svg-vector.svg"
westchester_burger_logo_url <- "https://www.westchesterburger.com/stamford/images/logo.png"


# Define a function to conditionally display the logos
conditional_logo <- function(restaurant_name) {
  if (restaurant_name == "McDonald's") {
    return(paste0('<img src="', mcdonalds_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Subway") {
    return(paste0('<img src="', subway_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Dunkin' Donuts") {
    return(paste0('<img src="', dunkin_donuts_logo_url, '" width="90px" height="100px">'))
  } else if (restaurant_name == "Burger King") {
    return(paste0('<img src="', burger_king_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Taco Bell") {
    return(paste0('<img src="', taco_bell_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "KFC") {
    return(paste0('<img src="', kfc_logo_url, '" width="140px" height="100px">'))
  } else if (restaurant_name == "Boston Market") {
    return(paste0('<img src="', boston_market_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Fuku") {
    return(paste0('<img src="', fuku_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Domino's Pizza") {
    return(paste0('<img src="', dominos_pizza_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Baskin-Robbins") {
    return(paste0('<img src="', baskin_robbins_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Panera Bread") {
    return(paste0('<img src="', panera_bread_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Wendy's") {
    return(paste0('<img src="', wendys_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Westchester Burger Company") {
    return(paste0('<img src="', westchester_burger_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Papa John's Pizza") {
    return(paste0('<img src="', papa_johns_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Chipotle Mexican Grill") {
    return(paste0('<img src="', chipotle_mexican_grill_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Little Caesars Pizza") {
    return(paste0('<img src"', little_caesars_pizza_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Popeyes") {
    return(paste0('<img src="', popeyes_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Five Guys") {
    return(paste0('<img src="', five_guys_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Sbarro") {
    return(paste0('<img src="', sbarro_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Git-It-N-Git") {
    return(paste0('<img src="', git_it_n_git_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "B. Good") {
    return(paste0('<img src="', b_good_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "31st Avenue Gyro") {
    return(paste0('<img src="', thirty_first_avenue_gyro_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Arby's") {
    return(paste0('<img src="', arbys_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Smashburger") {
    return(paste0('<img src="', smashburger_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "White Castle") {
    return(paste0('<img src="', white_castle_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Kennedy Fried Chicken & Pizza") {
    return(paste0('<img src="', kennedy_fried_chicken_pizza_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Dairy Queen") {
    return(paste0('<img src="', dairy_queen_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Blimpie") {
    return(paste0('<img src="', blimpie_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Nathan's Famous") {
    return(paste0('<img src="', nathans_famous_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Pizza Hut") {
    return(paste0('<img src="', pizza_hut_logo_url, '" width="100px" height="100px">'))
  } else if (restaurant_name == "Wendy's") {
    return(paste0('<img src="', wendys_logo_url, '" width="410" height="100px">'))
  } else {
    return("")
  }
}


# Create Leaflet map with marker cluster option
FastFoodRestaurants_NY_map <- leaflet(FastFoodRestaurants_NY) %>%
  addTiles() %>%
  addAwesomeMarkers(lng = ~longitude, lat = ~latitude,
                    icon = ~awesomeIcons(
                      icon = 'star',  # Choose an icon shape
                      library = 'fa', # Choose an icon library
                      markerColor = color_palette(FastFoodRestaurants_NY$name) # Set marker color based on "name" column
                    ),
                    popup = paste("Name:", FastFoodRestaurants_NY$name, "<br>",
                                  "Address:", FastFoodRestaurants_NY$address, "<br>",
                                  "City:", FastFoodRestaurants_NY$city, "<br>",
                                  "Province:", FastFoodRestaurants_NY$province, "<br>",
                                  "Postal Code:", FastFoodRestaurants_NY$postalCode, "<br>",
                                  sapply(FastFoodRestaurants_NY$name, conditional_logo)), # Add hosted image to the popup
                    clusterOptions = markerClusterOptions()) %>%
  setView(lng = -74.0060, lat = 40.7128, zoom = 10)  # Set initial map view to the center of New York City

# Display the map
FastFoodRestaurants_NY_map


```

### Wordcloud
```{r, message = FALSE, warning = FALSE}

# Read the dataset
data <- read.csv("/Users/justin/Downloads/US_Fast_Food_Restaurants - Sheet1.csv")

# Clean and preprocess the names
data_clean <- data %>%
  mutate(name = str_to_lower(name)) %>%
  mutate(name = str_replace_all(name, "[[:punct:]]", "")) %>%
  mutate(name = str_trim(name))

# Calculate the word frequencies
word_freq <- data_clean %>%
  count(name, sort = TRUE)

# Add percentage for restaurant count
word_freq <- word_freq %>%
  mutate(percentage = (n / sum(n)) * 100)

# Combine restaurant name and percentage
word_freq <- word_freq %>%
  mutate(word = paste0(name, " (", round(percentage, 2), "%)"))

# Create interactive word cloud
wordcloud2(data = word_freq, size = 0.5, color = "random-light", backgroundColor = "white")
```

### Changes in Food Prices over Time
```{r, message = FALSE, warning = FALSE}

foods <- read.table("/Users/justin/Downloads/FAOFP1990_2022.csv")
# Convert the year column to a date format
foods$Date <- dmy(foods$Date)

# Convert wide format to long format
foods_long <- pivot_longer(foods, 
                           cols = -Date, 
                           names_to = "Food_Group", 
                           values_to = "Price")

# Create line plot of food prices over time
ggplot(foods_long, aes(x = Date, y = Price, color = Food_Group)) +
  geom_line(size = 1) +
  scale_x_date(date_labels = "%Y", date_breaks = "2 years") +
  labs(x = NULL, y = "Price (USD)", 
       title = "Changes in Food Prices over Time",
       color = "Food Group") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "bottom",
        legend.title = element_text(face = "bold"),
        legend.text = element_text(size = 10),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"))
```

### Relationship between Healthcare Spending and Life Expectancy
```{r, message = FALSE, warning = FALSE}
# Create the ggplot object
# Import dataset
life <- read_excel("/Users/justin/Downloads/812013161P1G003.XLS", 
    sheet = "Data1.1.3", skip = 6)
life <- life[c(-4,-6)]
names(life) <- c("country","code","life_expectancy","Health_spending")
life <- na.omit(life)
life$country_name <- countrycode(life$code, "iso2c", "country.name")

# Create a vector of country codes to label
selected_countries <- c("US", "CN", "GB", "FR", "MX", "BR", "ZA")

# Create the ggplot object
p <- ggplot(life, aes(x = Health_spending, y = life_expectancy)) +
  geom_point(color = "red", shape = 17, size = 3) +
  labs(title = "Relationship between Healthcare Spending and Life Expectancy",
       x = "Total Healthcare Expenditure",
       y = "Life Expectancy (years)") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title = element_text(face = "bold"),
        axis.text = element_text(size = 10),
        legend.position = "bottom",
        legend.title = element_text(face = "bold"),
        legend.text = element_text(size = 10)) +
  geom_smooth(se = FALSE, color = "black") +
  
  #Add flag icon to the selected countries
  geom_flag(data = life[life$code %in% selected_countries,], aes(image = code), size = 0.03)

# Display the plot
print(p)
```


## Potential Solutions
### Food Availability per Capita over the Years

```{r, message = FALSE, warning = FALSE}
fruits_per_capita_availability <- read.csv('/Users/justin/Downloads/drive-download-20230503T032305Z-001/Fruits_Per capita availability adjusted for loss.csv')

vegetables_per_capita_availability <- read.csv('/Users/justin/Downloads/drive-download-20230503T032305Z-001/Vegetables_Per capita availability adjusted for loss.csv')

cheese_n_redmeat_per_capita_availability <- read.csv('/Users/justin/Downloads/drive-download-20230503T032305Z-001/Cheese_n_RedMeat_Per capita availability adjusted for loss.csv')

national_school_lunch <- read.csv("/Users/justin/Downloads/drive-download-20230503T032305Z-001/NATIONAL SCHOOL LUNCH PROGRAM.csv")

national_school_lunch_by_year <- read.csv("/Users/justin/Downloads/drive-download-20230503T032305Z-001/NATIONAL SCHOOL LUNCH PROGRAM By Year.csv")

child_n_adult_care_food <- read.csv("/Users/justin/Downloads/drive-download-20230503T032305Z-001/CHILD AND ADULT CARE FOOD PROGRAM.csv")

child_n_adult_care_food_by_year <- read.csv("/Users/justin/Downloads/drive-download-20230503T032305Z-001/CHILD AND ADULT CARE FOOD PROGRAM_by_year.csv")

  fruits_per_capita_availability %>%
  left_join(vegetables_per_capita_availability, by = 'Year') %>%
  select('Year','Lbs.year.x','Lbs.year.y') %>%
  rename('fruits'='Lbs.year.x', 'vegetables' = 'Lbs.year.y') %>%
  left_join(cheese_n_redmeat_per_capita_availability, by = 'Year') %>%
  ggplot(aes(x = Year)) +
  geom_line(aes(y = fruits, color = "fruits")) +
  geom_line(aes(y = vegetables, color = "vegetables")) +
  geom_line(aes(y = cheese, color = "cheese")) +
  geom_line(aes(y = red.meat, color = "red.meat")) +
  xlab("Year") +
  ylab("Lbs per capita") +
  scale_color_manual(values = c("fruits" = "blue", "vegetables" = "green", "cheese" = "pink", "red.meat" = "red")) +
  ggtitle("Food Availability per Capita over the Years")

```

### National School Lunch By Year
```{r, message = FALSE, warning = FALSE}
national_school_lunch_by_year$Total.Lunches.Served..millions. <- as.numeric(national_school_lunch_by_year$Total.Lunches.Served..millions.)

national_school_lunch_by_year$Percent.Free.RP <- as.numeric(national_school_lunch_by_year$Percent.Free.RP)


national_school_lunch_by_year %>%
  ggplot(aes(x = Year)) +
  geom_col(aes(y = Total.Lunches.Served..millions., fill = "Total Lunches")) +
  geom_line(aes(y = Percent.Free.RP*40, color = "Percent Free/Reduced"), size = 1.2) +
  xlab("Year") +
  ylab("Total Lunches Served (millions)") +
  scale_y_continuous(sec.axis = sec_axis(~ . / 40, name = "% Free/Reduced")) +
  ggtitle("National School Lunch By Year") +
  scale_fill_manual(values = "skyblue") +
  scale_color_manual(values = "orange") +
  theme(legend.title = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_line(colour = "gray", size = 0.5),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.y.right = element_text(size = 14, color = "orange"),
        axis.title.y.left = element_text(size = 14, color = "skyblue"))

```


### Special Diets Among Adults in the US from 2007 to 2018
```{r, message = FALSE, warning = FALSE}
library(RColorBrewer)
library(plotly)

diet_data <- data.frame(
  SurveyPeriod = c("2007–2008", "2009–2010", "2011–2012", "2013–2014", "2015–2016", "2017–2018"),
  AnySpecialDiet = c(14.3, 14.9, 14.4, 17, 16.5, 17.4),
  WeightLossDiet = c(7.5, 8.8, 8.8, 9.2, 8.7, 10),
  DiabeticDiet = c(1.8, 2.4, 1.9, 2, 2.1, 2.2),
  LowCarbDiet = c(0.9, 0.9, 0.9, 1.5, 1.7, 2.2),
  LowFatDiet = c(2.7, 1.9, 1.6, 2.1, 1.9, 1.5)
)

plot <- plot_ly(data = diet_data, x = ~SurveyPeriod, y = ~AnySpecialDiet, type = "scatter", mode = "lines+markers", name = "Any Special Diet", line = list(color = "blue"))
plot <- plot %>% add_trace(y = ~WeightLossDiet, name = "Weight Loss or Low Calorie Diet", line = list(color = "red"))
plot <- plot %>% add_trace(y = ~DiabeticDiet, name = "Diabetic Diet", line = list(color = "green"))
plot <- plot %>% add_trace(y = ~LowCarbDiet, name = "Low Carbohydrate Diet", line = list(color = "purple"))
plot <- plot %>% add_trace(y = ~LowFatDiet, name = "Low Fat or Low Cholesterol Diet", line = list(color = "orange"))

plot <- plot %>% layout(title = "Special Diets Among Adults in the US from 2007 to 2018",
                         xaxis = list(title = "Survey Period"),
                         yaxis = list(title = "Percentage(%)"))

plot
```

### Distribution of Dietary Habit Scores by Age Group
```{r, message = FALSE, warning = FALSE}
df <- read.csv("/Users/justin/Downloads/df.csv")

df |>
  group_by(age) |>
  mutate(med_d = round(median(d_number_total),2)) |>
  ggplot(aes(x=age, y= d_number_total)) +
  geom_boxplot() + 
  theme_minimal() + 
  geom_text(aes(x = age, y = med_d, label= med_d),
            vjust = -0.5, size = 3) +
  labs(x = "Age Group", y= "Total Score", title = "Distribution of Dietary Habit
       Scores by Age Group")
```

### Dietary Habits by Age Group
```{r, message = FALSE, warning = FALSE}
ppal <- c(
'#B5E48C',
'#52B69A',
'#168AAD',
'#184E77'
)

df |>
  select(age:household_income, d2:d5) |>
  rename("Sweetened Beverages"= d2, "Pre-made Meals"= d3, "Fast Food / Take-out"= d4,
         "Processed Snack Foods"= d5) |>
  pivot_longer(`Sweetened Beverages`: `Processed Snack Foods`, names_to = "question",
               values_to = "response") |>
  mutate(response = factor(response, levels=c('At least once daily', '3 to 5 times a week',
                                              '3 to 5 times a month', 'Once a month or less'))) |>
  ggplot(aes(x =age, fill = response)) +
  geom_bar(position='fill') + 
  facet_wrap(~question) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_fill_manual(values = ppal) + 
  scale_y_continuous(labels = scales::percent) + 
  labs(x = 'Age Group', y='Percentage', fill='Frequency',
       title = 'Dietary Habits by Age Group')
```
### Education - How it starts with you (Nutritional information on the most popular food, food type, and its respective calories)
```{r}
# Read the data
df <- read.csv("/Users/justin/Downloads/nutrients_new.csv", header = FALSE, skip = 2)

# Rename columns
colnames(df) <- c("Food Name", "Measure", "Grams", "Calories(kcal)", "Protein(g)", "Fat(g)", "Saturated Fat(g)", "Fiber(g)",
                 "Carbohydrates(g)", "Category")

# Format numeric columns
df_formatted <- df %>%
  mutate(across(where(is.numeric), round, 2))

# Create a color palette for the categories
unique_categories <- unique(df_formatted$Category)
color_palette <- colorRampPalette(brewer.pal(9, "Set1"))(length(unique_categories))
names(color_palette) <- unique_categories

# Apply the category colors to the dataframe
df_formatted$CategoryColor <- color_palette[df_formatted$Category]

# Create an interactive table using DT
datatable(df_formatted[, -which(names(df_formatted) == "CategoryColor")], # remove the "CategoryColor" column
          options = list(pageLength = 10, dom = 'Bfrtip', buttons = c('csv', 'excel', 'pdf', 'print')),
          rownames = FALSE,
          caption = tags$caption(tags$style(HTML("caption {font-size: 1.5em; font-weight: bold;}")),
                                 "Nutrient Data for Various Foods"),
          extensions = c('Buttons')) %>%
  formatStyle(names(df_formatted)[-which(names(df_formatted) == "CategoryColor")], # remove the "CategoryColor" column from names(df_formatted)
              fontWeight = styleEqual(names(df_formatted)[-which(names(df_formatted) == "CategoryColor")], "bold"),
              backgroundColor = styleEqual(names(df_formatted)[-which(names(df_formatted) == "CategoryColor")], "lightblue")) %>%
  formatStyle("Food Name",
              color = "black",
              fontWeight = "bold") %>%
  formatStyle(1:nrow(df_formatted), # color the entire row based on the "CategoryColor" column
              backgroundColor = styleEqual(df_formatted$CategoryColor, df_formatted$CategoryColor),
              include = TRUE)
```




